### 2019-04-05 thesis-template/msc-thesis.tex
update code
updatre

Principal Component Analysis is an algorithm to find the principal components (directions) in stochastic data. But it works similarly on transformations to find the principal directions on rotation and scaling. Now, principal component analysis can be done by eigenvalue or singular vector decomposition, whereas the former yields complex eigenvalues for asymmetric matrices. For (anti-)symmetric (normal) matrices, they are connected through the following relation: $s_i = \sqrt{|\lambda_i|}$. Mathematically speaking, a decomposition is somehow decomposing a transformation (which follows certain transformation rules) into parts of subsequent transformations consistent of rotation and scaling ($\mathbf{A} = \mathbf{R}\mathbf{S}\mathbf{R}^*$). We choose to use singular value decomposition ($\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^*$) to be able to set up real eigenvalues for any kind of matrix (singular values are always real and positive). Also, the singular vectors of the $\mathbf{U}$-matrix represent the half-axes of the principal ellipsoid (eigenframe) shown in Fig. \ref{HAT} for any kind of matrix as suggested by \cite{moler}. In addition, we also calculate the eigenvalues to exploit the sign of the real part of the eigenvalues ordered decreasingly by absolute value (corresponding to singular value order). The sign corresponds to tensile ($+$) and compressive ($-$) stress, which allows us to visualize deformation glyphs with arrows pointing inwards for compressive and outwards for tensile stresses. We do this decomposition analysis once for each matrix and then store the precomputed results in a grid. The principal ellipsoid is also used as a transmission profile for the propagation scheme in symbolic form in a subequent step.
\vskip 5pt
\section{Related Work}
\label{sec:related}

@@

Note that the resulting scalar field is $(n+1)$-dimensional ($x,y,z$ and direction $\theta$) and needs to be flattened by averaging or projection in 3D for proper visualization.

Dieses Kapitel stellt meist den Hauptteil der Arbeit dar. Vor dem
ersten Abschnitt sollte ein kurzer Überblick (ein paar wenige Sätze
mit Verweise auf nachfolgende Abschnitte) gegeben werden. Beispiel: Im
nachfolgenden Abschnitt \ref{sec:overview} wir ein Überblick über die Anforderungen an
das Modell gegeben.

\section{Outline and Ambitions}
\label{sec:overview}

Knapp zwei Seiten, in dem die Anforderungen, die Zielsetzung und die
Methoden überblicksartig beschrieben werden. Hier sollte die
Beschreibung ``technischer'' bzw.~``formaler'' sein als in der
Einleitung, da der Leser nun mit den Grundlagen und verwandten
Arbeiten vertraut ist.

@@

\section{Global Illumination Gradient}
\label{sec:ftle}

Usw.

>>>>

Principal Component Analysis is an algorithm which can capture the principal components (directions) in stochastic data. But it works similarly on transformations to find the principal directions on rotation and scaling. Now, principal component analysis can be done by eigenvalue or singular vector decomposition, whereas the former yields complex eigenvalues for asymmetric matrices. For (anti-)symmetric (normal) matrices, they are connected through the following relation: $s_i = \sqrt{|\lambda_i|}$. Mathematically speaking, a decomposition is somehow decomposing a transformation (which follows certain transformation rules) into parts of subsequent transformations consistent of rotation and scaling ($\mathbf{A} = \mathbf{R}\mathbf{S}\mathbf{R}^*$). We choose to use singular value decomposition ($\mathbf{A} = \mathbf{U} \mathbf{\Sigma} \mathbf{V}^*$) to be able to set up real eigenvalues for any kind of matrix (singular values are always real and positive). Also, the singular vectors of the $\mathbf{U}$-matrix represent the half-axes of the principal ellipsoid (eigenframe) shown in Fig. \ref{HAT} for any kind of matrix as suggested by \cite{moler}. In addition, we also calculate the eigenvalues to exploit the sign of the real part of the eigenvalues ordered decreasingly by absolute value (corresponding to singular value order). The sign corresponds to tensile ($+$) and compressive ($-$) stress, which allows us to visualize deformation glyphs with arrows pointing inwards for compressive and outwards for tensile stresses. We do this decomposition analysis once for each matrix and then store the precomputed results in a grid. The principal ellipsoid is also used as a transmission profile for the propagation scheme in symbolic form in a subequent step.
\vskip 5pt
\section{Related Work}
\label{sec:related}

@@

This chapter will summarize the main contributions of this work studied and state targeted aims and goals as a first step in sect. \ref{sec:overview}. Then we will have a short introduction to the implemented global illumination scheme derived and simplified from an nVidia GI approach in sect. \ref{sec:scheme}. Last, we will state the effectively developed Visualization methods GIGradient and Deformation Glyphs.

%Dieses Kapitel stellt meist den Hauptteil der Arbeit dar. Vor dem
%ersten Abschnitt sollte ein kurzer Überblick (ein paar wenige Sätze
%mit Verweise auf nachfolgende Abschnitte) gegeben werden. Beispiel: Im
%nachfolgenden Abschnitt \ref{sec:overview} wir ein Überblick über die Anforderungen an
%das Modell gegeben.

\section{Requirements and Ambitions}
\label{sec:spec}

develop a simple and efficient Global Illumination Scheme able to distribute energy profiles in discrete polar form in 2D/3D-space w.r.t. energy conservation and propagation attenuation principles;
able to handle any kind of matrix (symm./anti-symm.); generate transmission profiles; generate a new FTLE-related method for tensor field vis. by applying GIGradient;  be able to efficiently handle (relatively) large datasets; 
Knapp zwei Seiten, in dem die Anforderungen, die Zielsetzung und die
Methoden überblicksartig beschrieben werden. Hier sollte die
Beschreibung ``technischer'' bzw.~``formaler'' sein als in der
Einleitung, da der Leser nun mit den Grundlagen und verwandten
Arbeiten vertraut ist.

@@

\section{Global Illumination Gradient}
\label{sec:ftle}
Note that the resulting scalar field is $(n+1)$-dimensional ($x,y,z$ and direction $\theta$) and needs to be flattened by averaging or projection in 3D for proper visualization. 
Usw.
